An algorithm for searching the global minimum of univariate discontinuous functions\thanks{This study was supported by the Russian Science Foundation, project No.\,21-11-00204.}

### 2021-06-11 2021/ICCS_BarkalovUsova/iccs.tex
Add ORCID

\begin{document}
%
\title{An algorithm for searching the global minimum of univariate discontinuous functions\thanks{This work was supported by the Ministry of Science and Higher Education of the Russian Federation, project no. 0729-2020-0055, and by the Research and Education Mathematical Center, project no. 075-02-2020-1483/1.}}
%
\titlerunning{An algorithm for searching the global minimum}
% If the paper title is too long for the running head, you can set 
% an abbreviated paper title here
%
\author{Konstantin Barkalov %\orcidID{0000-0001-5273-2471}  
\and Marina Usova %\orcidID{0000-0002-8736-0652}
}
%
\authorrunning{K. Barkalov, M. Usova}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, 
Russia \email{konstantin.barkalov@itmm.unn.ru}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
We consider the problem of finding the global minimum of a one-dimensional function that may have several finite jump discontinuity points. The discontinuities of the objective function can reflect the specifics of the optimized object in the mathematical model (for example, shock effects, resonance phenomena, jumps in geometric dimensions or material properties, etc.). In some cases, the discontinuing set is known. However, at the same time, there are problems in which there are no a priori estimates of discontinuity points, but it is known that such points are possible. The paper gives a description of the global search algorithm for solving the specified class of problems. The authors conducted an experimental comparison of the proposed algorithm with the methods implemented in MATLAB Global Optimization Toolbox.

@@

\begin{figure}[!ht]
	\begin{center}
			\includegraphics[width=0.9\linewidth]{ris_1.jpg}
			\caption{Discontinuous objective function graph and trial points in case of given discontinuity points}
      \label{ris1}
	\end{center}
\end{figure}

>>>>

\begin{document}
%
\title{An algorithm for searching the global minimum of univariate discontinuous functions\thanks{This study was supported by the Russian Science Foundation, project No.\,21-11-00204.}}
%
\titlerunning{An algorithm for searching the global minimum}
% If the paper title is too long for the running head, you can set 
% an abbreviated paper title here
%
\author{Konstantin Barkalov \orcidID{0000-0001-5273-2471}  
\and Marina Usova \orcidID{0000-0002-0722-6884}
}
%
\authorrunning{K. Barkalov, M. Usova}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, 
Russia \email{konstantin.barkalov@itmm.unn.ru}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
We consider the problem of finding the global minimum of a one-dimensional function that may have several finite jump discontinuity points. The discontinuities of the objective function can reflect the specifics of the optimized object in the mathematical model (for example, shock effects, resonance phenomena, jumps in geometric dimensions or material properties, etc.). In some cases, the discontinuing set is known. However, at the same time, there are problems in which there are no a priori estimates of discontinuity points, but it is known that such points are possible. The paper gives a description of the global search algorithm for solving the specified class of problems. The authors conducted an experimental comparison of the proposed algorithm with the methods implemented in MATLAB Global Optimization Toolbox.

@@

\begin{figure}[ht]
	\begin{center}
			\includegraphics[width=0.9\linewidth]{ris_1.jpg}
			\caption{Discontinuous objective function graph and trial points in case of given discontinuity points}
      \label{ris1}
	\end{center}
\end{figure}
